---
title: "Devin Drummer Assignment 2 (2.1, 2.2)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
#Libraries
library(ggpubr)

data("airquality")
knitr::kable(head(airquality))

#Cor test for data

Results<-cor(airquality, method = "pearson", use = "complete.obs")

Results

#GGscatter plot

ggpubr::ggscatter(airquality, x = "Ozone", y = "Temp",
          add = "reg.line",  # Add regression line
          conf.int = TRUE,   # Add confidence interval
          add.params = list(color = "blue",
                            fill = "lightgray")
          )+ labs(title="Highest Correlation")+
  stat_cor(method = "pearson", label.x = 3, label.y = 30)

ggsave("Assignment 2 Problem 1.pdf")


ggplot(mtcars, aes(x=wt, y=mpg)) + 
  geom_point()+
  geom_smooth(method=lm)
```


```{bash}
#example I pulled from biostars

awk '/^>/ {printf("%s%s\t",(N>0?"\n":""),$0);N++;next;} {printf("%s",$0);} END {printf("\n");}' < myseqs.fasta > linear.fasta

while read IDS ; do grep "\b$IDS\b" linear.fasta ; done < listofids.txt
```





```{bash}


```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
