---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```


```{r}


```


```{bash}
#Download data
wget ftp://ftp.ncbi.nih.gov/blast/matrices/BLOSUM62

## I then used the import dataset dropdown in bring in the df from terminal
```


```{r}
#Rename for ease
df<- BLOSUM62

library(Biostrings)



```


```{r}
## Nucleotide global, local, and overlap alignments
  ## Nucleotide global, local, and overlap alignments
  P1 <- 
    ("AFVVTDNCIKCKYTDCVEVCPVDCFYEGPNFLVIHPDECIDCALCEPECPAQAIFSEDEVPEDMQEIQLNAELAEVWPNITEKKDPLPDAEDWDGVKGKLQHLER")

  P2 <-
    proString("AYVINDSC--IACGACKPECPVNIIQGS--IYAIDADSCIDCGSCASVC")


  # First use a fixed substitution matrix
  mat <- BLOSUM62(match = 1, mismatch = -3, baseOnly = TRUE)
  globalAlign <-
    pairwiseAlignment(P1, P2, substitutionMatrix = mat,
                      gapOpening = 5, gapExtension = 2)
  localAlign <-
    pairwiseAlignment(P1, P2, type = "local", substitutionMatrix = mat,
                      gapOpening = 5, gapExtension = 2)
  overlapAlign <-
    pairwiseAlignment(s1, s2, type = "overlap", substitutionMatrix = mat,
                      gapOpening = 5, gapExtension = 2)

  # Then use quality-based method for generating a substitution matrix
  pairwiseAlignment(P1, P2,
                    patternQuality = SolexaQuality(rep(c(22L, 12L), times = c(36, 18))),
                    subjectQuality = SolexaQuality(rep(c(22L, 12L), times = c(40, 20))),
                    scoreOnly = TRUE)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
