---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{bash}
#Download data for Assignment 1
wget ftp://ftp.ebi.ac.uk/pub/databases/Pfam/current_release/proteomes/

ls
```


```{bash}
#Determine how man domain types are in the human genome

cat ./index.html | cut -f6 | sort | uniq|wc -l
```


```{bash}
#Download bacterial Yersinia_pestis proteome 

wget -r -A.faa ftp://ftp.ncbi.nlm.nih.gov/genomes/archive/old_refseq/Bacteria/

#find faa 

find ftp.ncbi.nlm.nih.gov/ -name "*.faa"

ls
```


```{bash}
##Complete count
cat ../Yersinia_pestis | sort | uniq|wc -l
```


```{bash}
#Problem 4
## Download Data

wget ftp://ftp.ncbi.nlm.nih.gov/genomes/archive/old_refseq/Bacteria/Escherichia_coli_K_12_substr__MG1655_uid57779/NC_000913.faa
```


```{bash}
##Count the characters
cat NC_000913.faa | grep "^>" | wc -l

##Average length of protein

cat NC_000913.faa | grep -v "^>" | wc

###Number of character length
cat NC_000913.faa | grep -v "^>" | wc -c

###Get rid of returns and get final num
cat NC_000913.faa | grep -v "^>" | tr -d "\n" | wc -c

### Calculate 

echo $(cat NC_000913.faa | grep -v "^>" | tr -d "\n" | wc -c)/$(cat NC_000913.faa | grep "^>" | wc -l) |bc
```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
