---
title: "Assignment_3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Problem 1####
The PFAM domain distribution for human proteome can be found at ftp://ftp.ebi.ac.uk/pub/databases/Pfam/current_release/proteomes/9606.tsv.gz. The first column of this file is the protein accession number. The location of the domain hit for each gene is given by the columns 2-5. Columns 2-3 are alignment start and end. Columns 4-5 are envelope start and end. Envelopes are generally considered the location of a domain on a gene. Write a R scrpt that takes 9606.tsv.gz file as a first argument, a protein accession number as a second argument, and a location (integer) as a third argument. The program should print the domain name (hmm_name), if the location falls within a domain for a given protein accession. The program should return nothing if the position is outside the boundaries of domains. We should be able to run the program like this

> problem1.R ../data/9606.tsv.gz O95931 20
> Chromo

Hint: You should create a list using the protein accession as key and location start and end as values. You
might want to create a nested list or two separate lists.


```{bash}
curl -O ftp://ftp.ebi.ac.uk/pub/databases/Pfam/current_release/proteomes/9606.tsv.gz

#gunzip 9606.tsv.gz
```
```{r}
args <- commandArgs(trailingOnly = T)
file <- args[1] #"9606.tsv.gz"
accnum <- args[2] #"A0A024QZ18"
location <- as.integer(args[3]) #"75"

#I changed the example to one that would work


#gunzip and read in the file
#data_table = read.table(gzfile(paste0("./9606.tsv.gz")), header=F)
data_table = read.table(gzfile(paste(file)), header=F)

#filter for only the accnum of interest
#by_accnum = data_table[which(data_table[ ,1] == "A0A024QZ18"), ]
by_accnum = data_table[which(data_table[,1]==accnum),]


#extract and save envelope start and end
env_start=as.numeric(by_accnum[4])
env_end=as.numeric(by_accnum[5])


#if else statement to see if location is within envelope
#if(75>=env_start && 75<=env_end){
#  cat(paste0(as.matrix(by_accnum[7]),"\n"))
#}else{
#  break()
#}

if(location >= env_start && location <= env_end){
  cat(paste(as.matrix(by_accnum[7]),"\n"))
}else{
  break()
}

####script saved as problem3_1.R
```

```{bash}

#Run R scrip in bash
Rscript problem3_1.R "./9606.tsv.gz" A0A024QZ18 75
```


#####PROBLEM 2#####

Swissvar is a database of human gene, their variations, and disease associations. The file can be downloaded
from here: ftp://ftp.uniprot.org/pub/databases/uniprot/current_release/knowledgebase/variants/hu
msavar.txt. The 2nd column of the file is the protein accession numbers. These are the same accession
numbers used in the domain file in Problem 1. The 6th column is dbSNP and reports the variation at a
particular location. Using these two files, create a sorted list of domains according to the total number of
their variations. The domains with higher variations should be on top. The program should not take any
argument and output the domain list on STDOUT. The output should have two columns, separated by tab:
domain name (hmm_name) and a number indicating variation, like this:
Domain Variation
BRAC1 150
Chromo 100
...

```{r}
library(dplyr)

#download and parse swissvar 
swissvar_test <- read.table("./humsavar.txt", header = F, fill = T)
swissvar <- read.table("ftp://ftp.uniprot.org/pub/databases/uniprot/current_release/knowledgebase/variants/humsavar.txt",header = F,skip = 49, sep = "", fill = T, stringsAsFactors = F, flush = T,nrows=78710)

swissvar_clean<- swissvar[, -ncol(swissvar)]
colnames(swissvar_clean)=c("gene","accnum","FTId","change","variant","dbSNP")

#select for only needed data
swissvar_final <- swissvar_clean %>%
  select(gene,accnum, dbSNP)


##load and select domain file
domain_file = read.table(gzfile("9606.tsv.gz"))
colnames(domain_file) = c("accnum", "align_start", "align_end", "env_start", "env_end", "pfam", "hmm_name", "type", "V9", "V10", "V11", "V12", "V13", "V14")
domain_final <- domain_file %>%
  select(accnum, hmm_name)

join_test <- left_join(swissvar_final, domain_final)

 grouped_join <- join_test %>%
  group_by(hmm_name) %>%
  count(hmm_name)

colnames(grouped_join) = c("Domain", "Variation")

final_table <- grouped_join[order(-grouped_join$Variation),]

```

####Problem 3####

The first column of humsavar.txt file contains the gene name and the rest of the columns contains the other
information. Using this file (A) list out the top five genes that are mutated in various human disease. (B) plot
the frequency distribution of disease variants in human genome across all the genes in the file (C) calculate
the average number disease causing mutations across all genes in human genome and mark this number on
the previous plot as veritcal red line.
Hint: Remember to skip the information lines in the file and also note that type of variant column
contains both disease causing and non-disease causing variants.













