---
title: "Problem 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r engine = "bash"}
pwd
wget ftp://ftp.ebi.ac.uk/pub/databases/Pfam/current_release/proteomes/9606.tsv.gz
gunzip 9606.tsv.gz
```
```{r} 
#checking where I'm at
getwd()
list.files(getwd())
```


```{r}
#read the tsv file with colnames added manually, convert to aggregate list
pfam.table <- read.table("9606.tsv", sep = "\t", col.names = (c("seq id", "alignment start", 'alignment end', 'envelope start', "envelope end", "hmm acc", 'hmm name', 'type', 'hmm start', 'hmm end', 'hmm length', 'bit score', 'E-value', 'clan')))
head(pfam.table)
pfam.list<- as.list(pfam.table)
```
```{r}

#verifying that this function will give output if the given y is between to locations of envelope start and end
practice.function <- function(x, y) {
  if ((pfam.list$envelope.end[pfam.list$seq.id==x] >=y) & (pfam.list$envelope.start[pfam.list$seq.id==x] <=y)) 
    print("Okay")
}

practice.function("A0A024QZ18", "100")
pfam.list$envelope.start[seqid=="A0A024QZ18"]    
pfam.list$envelope.end[seqid=="A0A024QZ18"]
#function only works on the first instance of the seq.id...


practice.function2 <- function(x, y) {
  if ((pfam.list$envelope.end[pfam.list$seq.id==x] >=y) & (pfam.list$envelope.start[pfam.list$seq.id==x] <=y)) 
    print(pfam.list$hmm.name[pfam.list$seq.id==x,])
}

practice.function2("A0A024QZ18", "100")
#Doesn't work either

#another try..
args = commandArgs(trailingOnly = TRUE)
ptn.seq.id = args[1] 
location = args[2]

pfam.table <- read.table(gzfile("9606.tsv.gz"))

domain = pfam.table[which((pfam.table$seq.id == ptn.seq.id) & (pfam.table$envelope.start <= as.integer(location)) & (pfam.table$envelope.end >= as.integer(location))), ]

#doesn't work either.

```

